Social Computing Article\thanks{This title is temporary}

### 2013-01-17 Article.tex
arrumei umas coisas

\begin{abstract}
Social collaboration has been shown to facilitate problem-solving activity in a diverse set of environments. Nevertheless, if not well designed, a social human computation system may achieve results as poor as those of a single human subject performing a task. This scenario reflects a need for a better understanding of the performance issues of human problem-solving social networks. We present a novel method for agent-based social problem solving and test it against results with human subjects, analysing which parameters have effects on the performance of problem-solving social networks. Results show that evaluating neighbours' solutions in order to decide from which neighbour to copy is significantly better than selecting solutions based on their position on the graphic interface, as tests with human subjects have shown to be the preferred behaviour among people. Our results also indicate that copying and guessing are highly beneficial to the performance of these social networks. We then use these results to propose a collection of guidelines concerning the design of a efficient human computation system.
\end{abstract}

@@

We have developed and detailed a novel method for agent-based social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}. It was used it to built a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them. For simplicity, we limited our experiments to the {\em Sudoku} problem. Our goal is verifying whether the strategies employed by humans are competitive with other heuristics. After identifying the points in which those are lacking, we will then propose methods to increase the efficiency of human problem-solving networks.

@@

We developed a system in which the environment of the {\em Sudoku} problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments. We conceived a novel method for agent-based social problem solving which draws inspiration from the optimization technique of {\em Memetic Networks}~\cite{araujo:memenet}.

\section{A Novel Method for Agent-based Social Problem Solving}

A number of multi-agent methodologies that employ information flow through agents have been studied before. For instance, the {\em Memetic Networks} model proposed by~\cite{araujo:memenet} draws inspiration from the phenomenon of {\em Cultural Evolution} discussed by Dawkins in~\cite{dawkins:selfishgene} and has a network of agents sharing, copying and incrementing units of information in a similar way that nature, according to Dawkins, deals with {\em Memes}~\cite{dawkins:selfishgene}. Nevertheless, some aspects of social behaviour of great significance to social computing cannot be properly analysed through this methodologies. One example is the conformist behaviour studied in~\cite{cefferson:conformists} and~\cite{farenzena:collabem}. The proper study of these aspects demands a novel method for agent-based collaborative problem solving.

@@

In order to validate the algorithm as a social problem solving technique as well as establishing a comparison between agent-based simulations and tests with human subjects, we have modelled the collaborative {\em Sudoku} solving environment studied in~\cite{farenzena:collabem} through our method and tested it over a set of {\em Sudoku} instances.

@@

\begin{figure}
\includegraphics[scale=0.50]{progression}
\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)
}
\label{fig:progression}
\end{figure}

@@

We compared results from social computing experiments done with human subjects with agent-based simulations mimicking the same problem-solving environments. To do this, we proposed a novel method for agent-based social problem-solving and used it to model the {\em Sudoku} problem-solving environment studied by~\cite{farenzena:collabem}. We reached important conclusions concerning the dynamics of problem-solving collaborative environments: the behaviours of copying and guessing are shown to be beneficial to these systems. We also discuss the benefits of the behaviour of evaluating neighbours' solutions in order to select one of them for copying, rather than simply selecting a random solution or even the most readily available one, as the analysis conducted by~\cite{farenzena:collabem} has shown to be the case sometimes. Thus, having in mind the fact that the strategies employed by human subjects are often not the most efficient, we proposed a collection of guidelines concerning the design of human computation systems, which intend to improve the performance of the human subjects they employ.

>>>>

\begin{abstract}
Social collaboration has been shown to facilitate problem-solving activity in a diverse set of environments. Nevertheless, if not well designed, a social human computation system may achieve results as poor as those of a single human subject performing a task. This scenario reflects a need for a better understanding of the performance issues of human problem-solving social networks. We present a novel method for artificial social problem solving and test it against results with human subjects, analysing which parameters have effects on the performance of problem-solving social networks. Results show that evaluating neighbours' solutions in order to decide from which neighbour to copy is significantly better than selecting solutions based on their position on the graphic interface, as tests with human subjects have shown to be the preferred behaviour among people. Our results also indicate that copying and guessing are highly beneficial to the performance of these social networks. We then use these results to propose a collection of guidelines concerning the design of a efficient human computation system.
\end{abstract}

@@

We have developed and detailed a novel method for artificial social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}. It was used it to built a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them. For simplicity, we limited our experiments to the {\em Sudoku} problem. Our goal is verifying whether the strategies employed by humans are competitive with other heuristics. After identifying the points in which those are lacking, we will then propose methods to increase the efficiency of human problem-solving networks.

@@

We developed a system in which the environment of the {\em Sudoku} problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments. We conceived a novel method for artificial social problem solving which draws inspiration from the optimization technique of {\em Memetic Networks}~\cite{araujo:memenet}.

\section{A Novel Method for Artificial Social Problem Solving}

A number of multi-agent methodologies that employ information flow through agents have been studied before. For instance, the {\em Memetic Networks} model proposed by~\cite{araujo:memenet} draws inspiration from the phenomenon of {\em Cultural Evolution} discussed by Dawkins in~\cite{dawkins:selfishgene} and has a network of agents sharing, copying and incrementing units of information in a similar way that nature, according to Dawkins, deals with {\em Memes}~\cite{dawkins:selfishgene}. Nevertheless, some aspects of social behaviour of great significance to social computing cannot be properly analysed through this methodologies. One example is the conformist behaviour studied in~\cite{cefferson:conformists} and~\cite{farenzena:collabem}. The proper study of these aspects demands a novel method for artificial collaborative problem solving.

@@

In order to validate the algorithm as a social problem-solving technique, we have modelled the real-world collaborative {\em Sudoku} solving environment studied in~\cite{farenzena:collabem} through our method and tested it over a set of {\em Sudoku} instances, having in mind that the emergence of similar results as those observed by~\cite{farenzena:collabem} in their tests with {\em Sudoku} and {\em SAT} solving would validate our model as a good candidate for the design of social problem-solving simulations.

@@

\begin{figure}
\includegraphics[scale=0.47]{progression}
\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)
}
\label{fig:progression}
\end{figure}

@@

We compared results from social computing experiments done with human subjects with agent-based simulations mimicking the same problem-solving environments. To do this, we proposed a novel method for artificial social problem-solving and used it to model the {\em Sudoku} problem-solving environment studied by~\cite{farenzena:collabem}. We reached important conclusions concerning the dynamics of problem-solving collaborative environments: the behaviours of copying and guessing are shown to be beneficial to these systems. We also discuss the benefits of the behaviour of evaluating neighbours' solutions in order to select one of them for copying, rather than simply selecting a random solution or even the most readily available one, as the analysis conducted by~\cite{farenzena:collabem} has shown to be the case sometimes. Thus, having in mind the fact that the strategies employed by human subjects are often not the most efficient, we proposed a collection of guidelines concerning the design of human computation systems, which intend to improve the performance of the human subjects they employ.
